\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual Multi-Loop Integrands

### 2023-09-22 notes/2loopNLSM.tex
cleaned up conclusions

\subsection{One-loop color-dual integrands}\label{oneLoopCK}
\jm{Would it be alright to omit the coupling constants in this section?  I think we've done so elsewhere.}
Our first application of this theory for color-dual construction at
loop level is for self-dual Yang-Mills (SDYM). At tree-level, the
off-shell cubic vertices can be written in terms of light cone
coordinates \cite{Monteiro2011pc}:
\begin{equation}
X(p,k) = p_u k_w-p_w k_u
\end{equation}
At loop-level, this construction needs to be analytically continued to
general dimension in order to apply dimensional regularization at
one-loop. This can be done using the cubic semi-YM vertices of the
previous section:
\begin{equation} \label{DdimSDYM}
\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= \mathcal{X}(k_1,k_2) = (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3) -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3)
\end{equation}
Plugging in on-shell all-plus helicity states in light-cone gauge will
yield precisely the 4D SDYM vertex, up to an unphysical phase:
  \begin{equation}
  \mathcal{X}(k^+_1,k^+_2) = \frac{\langle 12\rangle^3}{ \langle23\rangle \langle 31\rangle} \sim \langle 12\rangle = k_{1,u} k_{2,w}-k_{1,w} k_{2,u}
 \end{equation}
where $\mathcal{X}(k^+_1,k^+_2) = A^{\text{YM}}(1^+,2^+,3^-)$ in light cone gauge, and in the second step applied momentum conservation to redefinition of the spinor bracket, $\langle 12\rangle \rightarrow X(p,k)$ defined in \cref{Conventions}. Of course, the form of \cref{DdimSDYM} has the advantage of
permitting a $D$-dimensional construction of the one-loop
integrand. Below we provide a four-point example:
\begin{equation}
\simplebox = g_{\text{YM}}^4 \langle \mathcal{X}(k_1,\ell_1)\mathcal{X}(k_2,\ell_2)\mathcal{X}(k_3,\ell_3)\mathcal{X}(k_4,\ell_4)\rangle
\end{equation}
where $\ell_i = \ell-(k_1+k_2+\cdots+ k_i)$ and the bracket $\langle \,\cdots\rangle$ indicates that we have applied the gauge fixed state projector, $\sum {\varepsilon^\mu_{(+\ell_i)}\varepsilon^\nu_{(-\ell_i)}}=\eta^{\mu\nu}$ on all internal polarizations.
In general, the $n$-gon diagram would be,
\begin{equation}
N^{\text{SDYM}}_{n\text{-gon}}= \nGonVector = g_{\text{YM}}^n \langle \mathcal{X}(k_1,\ell_1)\mathcal{X}(k_2,\ell_2)\cdots \mathcal{X}(k_n,\ell_n) \rangle
\end{equation}
Due to the state-sum of internal loop factors,
$\sum {\varepsilon_{(+\ell)}\varepsilon_{(-\ell)}}\sim D$, the integrand above
depends explicitly on the spacetime dimension, $D$. By taking a
derivative\footnote{Another way to understand this derivative is that
  it selects the large $D$ behavior of the integrand.}, we can recover
the integrand needed for all-plus one-loop amplitudes with an internal
scalar:
\begin{equation}
\partial_D N^{\text{SDYM}}_{n\text{-gon}}=\nGonScalar  = (2 g_{\text{YM}})^n (\ell_1 \varepsilon_1)(\ell_2 \varepsilon_2)\cdots (\ell_n \varepsilon_n)
\end{equation}
This integrand numerator with internal scalar loop is precisely what
one would obtain from the Feynman rules of $YZ$-theory, absent the $\bar{Z}Z$
internal vector loop. For more background, we refer the reader to
\cref{sec:CKLagrangians}. When plugging on the on-shell states of $YZ$-theory, we thus obtain the following expression for the NLSM one-loop $n$-gon numerator:
\begin{equation}
N^{\text{NLSM}}_{n\text{-gon}}=\left[\partial_D  N^{\text{SDYM}}_{n\text{-gon}}\right]^{\epsilon \rightarrow k}=\nGonScalar =  f_\pi^{-n} [12][23]\cdots [n1]
\end{equation}
Where we have define the antisymmetric kinematic variable,
$[ij] = \ell_i^2 - \ell_j^2$, since when plugging on longitudinal
modes, the $n$-gon can be re-expressed completely in terms of inverse
propagators, $2(k_i \cdot \ell_i) = \ell_{i}^2-\ell^2_{i-1}$. We have
verified through 10-point one-loop that this $n$-gon expression is a
valid color-dual representation for NLSM.

Before proceeding, we note that the above definition does give rise to ``pathological" bubble-on-external-leg (BEL) diagrams, discussed previously in \cref{sec:bootstrap}. However, one can show that these diagrams integrate to zero for spacetime dimension, $D>2$, and thus can be disregarded as unphysical. For the interested reader, in \cref{BELreg} we provide a detailed overview of this dimensional regularization of the BEL diagram.
\subsection{Two-loop obstruction}\label{2LoopObstruction}
At two-loop, introducing terms that conspire with four-point contacts
is unavoidable. At one-loop, we were able to avoid internal
contractions of $\bar{A}_\mu A^\mu$ by selecting appropriate external
states. However, at two-loop when choosing all external $A_\mu$
states, the amplitude vanishes in semi-YM theory:
\begin{equation}
\mathcal{A}^{\text{semi-YM}}_{\text{2-loop}}(A_\mu,A_\mu,A_\mu,A_\mu)=0
\end{equation}
In order to produce non-vanishing interactions, we would need to
reintroduce $D$-dimensional vertices from the diagonal group of
$G_L\times G_R$ that have the wrong weight. Doing so will necessarily permit internal
contractions of $\bar{A}_\mu A^\mu$,
\begin{equation}
\mathcal{A}^{\text{YM}}_{\text{2-loop}}(A_\mu,A_\mu,A_\mu,A_\mu)=\doubleBoxObstructionA +\doubleBoxObstructionB+\cdots 
\end{equation}
where we used white dots to indicate interaction vertices of
weight\footnote{We choose the convention that the abelianized gauge
  fields carry weight $\mathcal{W}[\bar{A}] = -1$, and non-abelian
  vectors are $\mathcal{W}[\bar{A}] = +1$.}
$\mathcal{W}[\bar{A}\bar{A} A] = -1$, rather than the isolated semi-YM
vertex which always carries weight $\mathcal{W}[\bar{A}A A] =
+1$. This immediately runs into the difficulty of introducing the
four-point contact needed for color-kinematics to be satisfied on all
internal edges. By a simple weight counting argument, one can see that
including this wrong sign interactions is unavoidable at two-loop and
higher.

@@

\section{Conclusions and Outlook}\label{conclusions}
In summary, we have found that there is a tension between color-kinematics duality and an off-shell local construction of the two-loop four-point of the pure Yang-Mills integrand in $D$-dimensions.
At tree level, we demonstrated that the duality can be
manifested by breaking manifest Bose symmetry at the Lagrangian level,
either by explicitly picking different gluon states (as in SDYM) or by
picking states that only restore Bose symmetry in the final amplitude
(as in NLSM).  All of these theories can be encapsulated in the
semi-abelian YM theory presented in \cref{eq:semiYM} which obscures
the Bose symmetry of the external states due to the presence of the
two gauge fields $A_\mu$ and $\bar{A}_\mu$.

In addition to the natural tree-level construction, we found that kinetic mixing
between the two gauge fields permits globally color-dual one-loop
integrands, but special care must be taken so that the integrands
produced from semi-abelian YM correspond to SDYM or NLSM.  Due to the
kinetic mixing that stems from the broken Bose symmetry, it is
impossible to construct a two-loop integrand for semi-abelian YM theory,
that is, the theory is one-loop exact.  Obtaining a globally color-dual
integrand beyond one-loop then requires sacrificing more than just Bose
symmetry and in this paper we have argued that off-shell locality must
be abandoned. \footnote{An example of this can already be found in the literature, where Locality is relaxed in \cite{Mogull:2015adi} in
  order to obtain color-dual two-loop integrands with on-shell 4D states.}

We concede building loop-level numerators from rational functions of the kinematics
is rather unnatural from the perspective of point-like quantum field
theories. After all, operators that produce rational functions are typically non-local in their construction. The archetypal example of non-local quantum operators are string vertex operators with $\alpha'$ corrections. These operators promote local tree-level amplitudes to stringy extended objects by integrating over the open string world-sheet:
\be
\mathcal{A}^{\text{YM}} \stackrel{\alpha'}{\longrightarrow} \mathcal{A}^{\text{OS}}t_8 F^4 \int_0^1 dx \,(1-x)^{\alpha' s_{12}-1} x^{\alpha' s_{12}-1}
\ee
The resulting Veneziano factor of Gamma functions produces rational functions of kinematics, while preserving the color-dual structure at in the color-ordering of the Park-Taylor factor in the denominator. While introducing a string world sheet is a jump from what we have found in this work, our funding certainly suggest that we must do \textit{something} to relax the constraint of
\textit{off-shell locality}, and realize locality only in the limit of
\textit{on-shell} kinematics. This could be acheived by either modifying the kinetic term or potentially something more exotic. Below we provide an overview of what one
might expect for such a construction, and provide some simple examples
at tree-level that manifest this structure.

\subsection{Non-local construction of scattering amplitudes}
\label{nonLocalScattering}
As an exemplar of an off-shell non-local construction, consider the simple four-point example of a color-dual
representation of Yang-Mills theory. We can define a functional numerator, $N_{(12|34)}^{\text{YM}}$, as follows, 
\begin{equation}
N_{(12|34)}^{\text{YM}} = \frac{t_8F^4}{3} \frac{s_{13}-s_{12}}{s_{23}{s_{13}}}
\end{equation}
where $N_s = N_{(12|34)}$, $N_t = N_{(14|23)}$ and $N_u = N_{(13|42)}$. By construction, this functionally symmetric numerator is
anti-symmetric and obeys the Jacobi identity:
\begin{equation}\label{nonLocalNum}
N_{(12|34)}^{\text{YM}} + N_{(13|42)}^{\text{YM}} +N_{(14|23)}^{\text{YM}} = 0
\end{equation}
However, it must also factorize to kinematics that are consistent with
the local Feynman rules of \cref{eq:ym-lag}. Evaluating the residue on
the $s=s_{12} \to 0$ pole we find:
\begin{align}
\text{Res}\left[\frac{ N_{s}^{\text{YM}} }{s}\right]^{s=0}&= \frac{2}{3}A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} 
\\
\text{Res}\left[\frac{N_{t}^{\text{YM}} }{t}\right]^{s=0}&= -\frac{1}{3}A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} 
\\
\text{Res}\left[\frac{N_{u}^{\text{YM}} }{u}\right]^{s=0}&= -\frac{1}{3} A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} 
\end{align}
with $t=s_{23}$ and $u=s_{13}$.
Plugging these into a cubic graph representation of Yang-Mills, the
tree level version of \cref{eq:gen-amp}, we find:
\begin{equation}
  \text{Res}\left[\mathcal{A}_4^{\text{YM}}\right]^{s=0}
  = \frac{1}{3} A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} (2c_s-c_t-c_u)
  =  \mathcal{A}_{(12|l)}^{\text{YM}}\mathcal{A}_{(-l|34)}^{\text{YM}} 
\end{equation}
where we have applied the color structure Jacobi identity,
$c_s+c_t+c_u=0$. In light of our findings in \cref{chefsKiss}, building color-dual numerators in this way where locality is only realized on-shell might be a more natural approach. While we can absolutely apply a generalized gauge
transformation \cite{BCJ} to restore field theoretic locality to the
cubic numerators, this could merely be an aesthetic choice that is only permissible at tree-level.

@@

\subsection{Future Directions}\label{sec:Discussion}
With an eye towards generalizing this construction for future multi-loop studies, we note that the four-point half-ladder secretly makes use of the color-dual structure of NLSM. At four-point, we can construct permutation invariants from the single BCJ basis amplitude of both NLSM and pure YM theory as follows:
\be
s t A^{\text{YM}}_{(s,t)} = t_8F^4 \qquad s t A^{\text{NLSM}}_{(s,t)} = s_{12}s_{23}s_{13}
\ee
Using this, we can redefine our non-local numerator of \cref{nonLocalNum} in a form that recasts color-dual structure to NLSM, and removes all the vector structure of Yang-Mills as an overall $t_8F^4$ factor:
\be
N_{(12|34)}^{\text{YM}} \equiv t_8F^4 \,\frac{N_{(12|34)}^{\text{NLSM}}}{s_{12}s_{23}s_{13}} 
\ee
One advantage of this construction is that reduces some of the $D$-dimensional complexity vector theories that arises due to the mixing between external polarization and
internal loop momenta. But maybe more importantly, it puts all the heavy lifting of functional jacobi relations on the scalar kinematic numerator, $N_{(12|34)}^{\text{NLSM}}$. Thus, rather
than building an ansatz from the irreducible scalar products of
\cref{eq:ym-basis}, one might instead consider the following construction
\begin{equation}
N^{\text{YM}}_{m,L} = \sum_i \mathcal{O}_i \mathcal{R}^{(i)}_{m,L}
\end{equation}
where $\mathcal{O}_i$ are the gauge invariant tensor basis elements of
\cite{Bern:2017tuc,Carrasco:2019yyn}, and $ \mathcal{R}^{(i)}_{m,L}$ are
rational functions of irreducible scalar products of \cref{eq:scalar-basis}. It would be interesting if a similar construction as our toy tree-level example could be uplifted to two-loop using the globally color-dual NLSM integrand that we have computed in this work. We see this as a natural future direction worth investigating that is made possible given the results of this work.

>>>>

\subsection{One-loop color-dual integrands}\label{oneLoopCK}
\jm{Would it be alright to omit the coupling constants in this section?  I think we've done so elsewhere.}
Our first application of this theory for color-dual construction at
loop level is for self-dual Yang-Mills (SDYM). At tree-level, the
off-shell cubic vertices can be written in terms of light cone
coordinates \cite{Monteiro2011pc}:
\begin{equation}
X(p,k) = p_u k_w-p_w k_u
\end{equation}
At loop-level, this construction needs to be analytically continued to
general dimension in order to apply dimensional regularization at
one-loop. This can be done using the cubic semi-YM vertices of the
previous section:
\begin{equation} \label{DdimSDYM}
\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= \mathcal{X}(k_1,k_2) = (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3) -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3)
\end{equation}
Plugging in on-shell all-plus helicity states in light-cone gauge will
yield precisely the 4D SDYM vertex, up to an unphysical phase:
  \begin{equation}
  \mathcal{X}(k^+_1,k^+_2) = \frac{\langle 12\rangle^3}{ \langle23\rangle \langle 31\rangle} \sim \langle 12\rangle = k_{1,u} k_{2,w}-k_{1,w} k_{2,u}
 \end{equation}
where $\mathcal{X}(k^+_1,k^+_2) = A^{\text{YM}}(1^+,2^+,3^-)$ in light cone gauge, and in the second step applied momentum conservation to redefinition of the spinor bracket, $\langle 12\rangle \rightarrow X(p,k)$ defined in \cref{Conventions}. Of course, the form of \cref{DdimSDYM} has the advantage of
permitting a $D$-dimensional construction of the one-loop
integrand. Below we provide a four-point example:
\begin{equation}
\simplebox = g_{\text{YM}}^4 \langle \mathcal{X}(k_1,\ell_1)\mathcal{X}(k_2,\ell_2)\mathcal{X}(k_3,\ell_3)\mathcal{X}(k_4,\ell_4)\rangle
\end{equation}
where $\ell_i = \ell-(k_1+k_2+\cdots+ k_i)$ and the bracket $\langle \,\cdots\rangle$ indicates that we have applied the gauge fixed state projector, $\sum {\varepsilon^\mu_{(+\ell_i)}\varepsilon^\nu_{(-\ell_i)}}=\eta^{\mu\nu}$ on all internal polarizations.
In general, the $n$-gon diagram would be,
\begin{equation}\label{SDYMnGon}
N^{\text{SDYM}}_{n\text{-gon}}= \nGonVector = g_{\text{YM}}^n \langle \mathcal{X}(k_1,\ell_1)\mathcal{X}(k_2,\ell_2)\cdots \mathcal{X}(k_n,\ell_n) \rangle
\end{equation}
Due to the state-sum of internal loop factors,
$\sum {\varepsilon_{(+\ell)}\varepsilon_{(-\ell)}}\sim D$, the integrand above
depends explicitly on the spacetime dimension, $D$. By taking a
derivative\footnote{Another way to understand this derivative is that
  it selects the large $D$ behavior of the integrand.}, we can recover
the integrand needed for all-plus one-loop amplitudes with an internal
scalar:
\begin{equation}
\partial_D N^{\text{SDYM}}_{n\text{-gon}}=\nGonScalar  = (2 g_{\text{YM}})^n (\ell_1 \varepsilon_1)(\ell_2 \varepsilon_2)\cdots (\ell_n \varepsilon_n)
\end{equation}
This integrand numerator with internal scalar loop is precisely what
one would obtain from the Feynman rules of $YZ$-theory, absent the $\bar{Z}Z$
internal vector loop. For more background, we refer the reader to
\cref{sec:CKLagrangians}. When plugging on the on-shell states of $YZ$-theory, we thus obtain the following expression for the NLSM one-loop $n$-gon numerator:
\begin{equation}\label{NLSMnGon}
N^{\text{NLSM}}_{n\text{-gon}}=\left[\partial_D  N^{\text{SDYM}}_{n\text{-gon}}\right]^{\epsilon \rightarrow k}=\nGonScalar =  f_\pi^{-n} [12][23]\cdots [n1]
\end{equation}
Where we have define the antisymmetric kinematic variable,
$[ij] = \ell_i^2 - \ell_j^2$, since when plugging on longitudinal
modes, the $n$-gon can be re-expressed completely in terms of inverse
propagators, $2(k_i \cdot \ell_i) = \ell_{i}^2-\ell^2_{i-1}$. We have
verified through 10-point one-loop that this $n$-gon expression is a
valid color-dual representation for NLSM.

Before proceeding, we note that the above definition does give rise to ``pathological" bubble-on-external-leg (BEL) diagrams, discussed previously in \cref{sec:bootstrap}. However, one can show that these diagrams integrate to zero for spacetime dimension, $D>2$, and thus can be disregarded as unphysical. For the interested reader, in \cref{BELreg} we provide a detailed overview of this dimensional regularization of the BEL diagram.
\subsection{Two-loop obstruction}\label{2LoopObstruction}
At two-loop, introducing terms that conspire with four-point contacts
is unavoidable. At one-loop, we were able to avoid internal
contractions of $\bar{A}_\mu A^\mu$ by selecting appropriate external
states. However, at two-loop when choosing all external $A_\mu$
states, the amplitude vanishes in semi-YM theory:
\begin{equation}
\mathcal{A}^{\text{semi-YM}}_{\text{2-loop}}(A_\mu,A_\mu,A_\mu,A_\mu)=0
\end{equation}
In order to produce non-vanishing interactions, we would need to
reintroduce $D$-dimensional vertices from the diagonal group of
$G_L\times G_R$ that have the wrong weight. Doing so will necessarily permit internal
contractions of $\bar{A}_\mu A^\mu$,
\begin{equation}\label{2loopTension}
\mathcal{A}^{\text{YM}}_{\text{2-loop}}(A_\mu,A_\mu,A_\mu,A_\mu)=\doubleBoxObstructionA +\doubleBoxObstructionB+\cdots 
\end{equation}
where we used white dots to indicate interaction vertices of
weight\footnote{We choose the convention that the abelianized gauge
  fields carry weight $\mathcal{W}[\bar{A}] = -1$, and non-abelian
  vectors are $\mathcal{W}[\bar{A}] = +1$.}
$\mathcal{W}[\bar{A}\bar{A} A] = -1$, rather than the isolated semi-YM
vertex which always carries weight $\mathcal{W}[\bar{A}A A] =
+1$. This immediately runs into the difficulty of introducing the
four-point contact needed for color-kinematics to be satisfied on all
internal edges. By a simple weight counting argument, one can see that
including this wrong sign interactions is unavoidable at two-loop and
higher.

@@

\section{Conclusions and Outlook}\label{conclusions}

In summary, we have found that there is a tension between color-kinematics duality and an off-shell local construction of the two-loop four-point pure Yang-Mills integrand in $D$-dimensions.
At tree level, we found that the duality can be
manifested by breaking manifest Bose symmetry at the Lagrangian level,
either by explicitly picking different gluon states (as in SDYM) or by
picking states that only restore Bose symmetry in the final amplitude
(as in NLSM).  All of these theories can be encapsulated in the
semi-abelian YM theory presented in \cref{eq:semiYM} which obscures
the Bose symmetry of the external states due to the presence of the
two gauge fields $A_\mu$ and $\bar{A}_\mu$.

In addition to the natural tree-level construction, we found that kinetic mixing
between the two gauge fields permits globally color-dual one-loop
integrands, and after plugging in suitable on-shell states, the integrands
produced by semi-abelian YM correspond are those of SDYM in \cref{SDYMnGon} 
and NLSM in \cref{NLSMnGon}.  Due to the
kinetic mixing that stems from the broken Bose symmetry, \cref{2loopTension} shows why it is
impossible to construct a two-loop integrand for semi-abelian YM theory. In \cref{2loopBoot}, we overcame this obstruction by successfully constructing two-loop NLSM numerators with an ansatz based bootstrap. However, we found that the same approach fails for two-loop pure Yang-Mills, and pin-pointed the failure point to a particular unitarity cut captured by \cref{chefsKiss}. Thus, obtaining a globally color-dual
integrand beyond one-loop then requires sacrificing more than just Bose
symmetry, and in this paper we have argued that off-shell locality must
be abandoned for color-dual constructions of multi-loop Yang-Mills. \footnote{An example of this can already be found in the literature, where Locality is relaxed in \cite{Mogull:2015adi} in
  order to obtain color-dual two-loop integrands with on-shell 4D states.} To expand the available function space, we propose that one should consider including rational functions of kinematics, rather than just polynomials.

We concede building loop-level numerators from rational functions of the kinematics
is rather unnatural from the perspective of point-like quantum field
theories. After all, operators that produce rational functions are typically non-local in their construction. The archetypal example of non-local quantum operators are string vertex operators with $\alpha'$ corrections. These operators promote local tree-level amplitudes to stringy extended objects by integrating over disc integrals of the open string worldsheet:
\be
\mathcal{A}^{\text{YM}} \stackrel{\alpha'}{\longrightarrow} \mathcal{A}^{\text{OS}}\supset t_8 F^4 \int_0^1 dx \,\frac{ x^{\alpha' s_{12}}(1-x)^{\alpha' s_{23}}}{x(1-x)(s_{12}+s_{23})}
\ee
The resulting Veneziano factor of Gamma functions produces rational functions of kinematics, while preserving the color-dual structure color and kinematic factors \cite{Carrasco:2019yyn}. While introducing some type of worldsheet formulation of color-dual numerators might seem unjustified given the results of this work, our findings certainly suggest that we must do \textit{something} to relax the constraint of off-shell locality, and realize locality only in the limit of
\textit{on-shell} kinematics. This could be acheived by either modifying the kinetic term or potentially something new and more exotic. Below we provide some simple examples
at tree-level of what one might consider for implementing such a construction.

\subsection{Non-local construction of scattering amplitudes}
\label{nonLocalScattering}
As an exemplar of an off-shell non-local structure, consider the simple four-point example of a color-dual
representation of Yang-Mills theory. We can define a functional numerator, $N_{(12|34)}^{\text{YM}}$, as follows, 
\begin{equation}
N_{(12|34)}^{\text{YM}} = \frac{t_8F^4}{3} \frac{s_{13}-s_{12}}{s_{23}{s_{13}}}
\end{equation}
where $N_s = N_{(12|34)}$, $N_t = N_{(14|23)}$ and $N_u = N_{(13|42)}$. By construction, this functionally symmetric numerator is
anti-symmetric and obeys the Jacobi identity:
\begin{equation}\label{nonLocalNum}
N_{(12|34)}^{\text{YM}} + N_{(13|42)}^{\text{YM}} +N_{(14|23)}^{\text{YM}} = 0
\end{equation}
However, it must also factorize to kinematics that are consistent with
the local Feynman rules of \cref{eq:ym-lag}. Evaluating the residue on
the $s=s_{12} \to 0$ pole we find:
\begin{align}
\text{Res}\left[\frac{ N_{s}^{\text{YM}} }{s}\right]^{s=0}&= \frac{2}{3}A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} 
\\
\text{Res}\left[\frac{N_{t}^{\text{YM}} }{t}\right]^{s=0}&= -\frac{1}{3}A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} 
\\
\text{Res}\left[\frac{N_{u}^{\text{YM}} }{u}\right]^{s=0}&= -\frac{1}{3} A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} 
\end{align}
with $t=s_{23}$ and $u=s_{13}$.
Plugging these into a cubic graph representation of Yang-Mills, the
tree level version of \cref{eq:gen-amp}, we find:
\begin{equation}
  \text{Res}\left[\mathcal{A}_4^{\text{YM}}\right]^{s=0}
  = \frac{1}{3} A_{(12|l)}^{\text{YM}}A_{(-l|34)}^{\text{YM}} (2c_s-c_t-c_u)
  =  \mathcal{A}_{(12|l)}^{\text{YM}}\mathcal{A}_{(-l|34)}^{\text{YM}} 
\end{equation}
where we have applied the color structure Jacobi identity,
$c_s+c_t+c_u=0$. In light of our findings in \cref{chefsKiss}, building color-dual numerators in this way where locality is only realized on-shell might be a more natural approach. While we can absolutely apply a generalized gauge
transformation \cite{BCJ} to restore field theoretic locality to the
cubic numerators, this could merely be an aesthetic choice that is only permissible at tree-level.

@@

\subsection{Future Directions}\label{sec:Discussion}
With an eye towards generalizing this construction for future multi-loop studies, we note that the four-point half-ladder secretly makes use of the color-dual structure of NLSM. At four-point, we can construct permutation invariants from the single BCJ basis amplitude of both NLSM and pure YM theory as follows:
\be
s t A^{\text{YM}}_{(s,t)} = t_8F^4 \qquad s t A^{\text{NLSM}}_{(s,t)} = s_{12}s_{23}s_{13}
\ee
Using this, we can redefine our non-local numerator of \cref{nonLocalNum} in a form that recasts color-dual structure to NLSM, and removes all the vector structure of Yang-Mills as an overall $t_8F^4$ factor:
\be
N_{(12|34)}^{\text{YM}} \equiv t_8F^4 \,\frac{N_{(12|34)}^{\text{NLSM}}}{s_{12}s_{23}s_{13}} 
\ee
One advantage of this construction is that it reduces some of the $D$-dimensional complexity of vector theories that arises due to the mixing between external polarization and
internal loop momenta. But maybe more importantly, it puts all the heavy lifting of functional Jacobi relations on the scalar kinematic numerator, $N_{(12|34)}^{\text{NLSM}}$. Thus, rather
than building an ansatz from the irreducible scalar products of
\cref{eq:ym-basis}, one might instead consider the following construction
\begin{equation}
N^{\text{YM}}_{m,L} = \sum_i \mathcal{O}_i \mathcal{R}^{(i)}_{m,L}
\end{equation}
where $\mathcal{O}_i$ are the on-shell gauge invariant tensor basis elements of
\cite{Bern:2017tuc,Carrasco:2019yyn}, and $ \mathcal{R}^{(i)}_{m,L}$ are
rational functions of irreducible scalar products of \cref{eq:scalar-basis}. It would be interesting if a similar construction as our tree-level example could be uplifted to two-loop using the globally color-dual NLSM integrand that we have computed in this work. We see this as a natural future direction worth investigating that is made possible given our findings.
